---
title: "EDA Kaggle Placements"
author: "Renaud Liber"
date: "10-6-2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries}

#devtools::install_github('bbc/bbplot')
#install.packages("GGally")

library(tidyverse)
library(janitor)
library(DataExplorer)
library(tidytext)
library(bbplot)
library(networkD3)
library(GGally)

theme_set(theme_light())

getwd()

```


```{r}
placement_raw <- read_csv("../00_Data/datasets_596958_1073629_Placement_Data_Full_Class.csv")
```





```{r}

placement <- placement_raw %>% 
  rename(Grade_Secondary        = ssc_p,
         Grade_Higher_Secondary = hsc_p,
         Spec_Higher_Secondary  = hsc_s,
         Grade_Degree           = degree_p,
         Spec_Degree            = degree_t,
         work_Experience        = workex,
         Grade_Employability    = etest_p,
         Spec_MBA               = specialisation,
         Grade_MBA              = mba_p,
         Placement_Status       = status,
         Salary                 = salary
        ) %>% 
  clean_names()

```




```{r}
glimpse(placement)
```


```{r}
placement %>% DataExplorer::plot_missing()
```

What are the most common degree 

```{r}
placement %>% 
  select(sl_no,starts_with("spec")) %>% 
  pivot_longer(contains("spec")) %>% 
  group_by(name,value) %>% 
  summarise(n_student=n()) %>% 
  arrange(-n_student) %>% 
  ungroup() %>% 
  mutate(name=name %>% str_remove("spec_") %>% str_replace("_"," ") %>% str_to_title() %>% str_replace("Mba","MBA"),
          value=reorder_within(value,by=n_student,within = name)) %>% 
  ggplot(aes(value,n_student,fill=name))+
  geom_col()+
  facet_wrap(~name,scales = "free")+
  coord_flip()+ 
  scale_x_reordered()+ # Argument is key to have a nice x axis
  labs(title = "Student Specialisation by Degree",
       y="Number of Students")
  

```



```{r}
MoveHStoD <- placement %>% 
  group_by(spec_higher_secondary,spec_degree) %>% 
  summarise(value=n()) %>% 
  ungroup() %>% 
  rename(source=spec_higher_secondary,
         target=spec_degree)

MBAtoPlacement <- placement %>% 
  group_by(spec_mba,placement_status) %>% 
  summarise(value=n()) %>% 
  ungroup() %>% 
  rename(source=spec_mba,
         target=placement_status)


Links_source <- placement %>% 
  group_by(spec_degree,spec_mba) %>% 
  summarise(value=n()) %>% 
  ungroup() %>% 
  rename(source=spec_degree,
         target=spec_mba,
         ) %>% 
  bind_rows(MoveHStoD) %>% 
  bind_rows(MBAtoPlacement)


temp_ls <- Links_source %>% select(source, target)


listing <- data.frame(name=unlist(temp_ls,use.names = FALSE)) %>% 
    distinct() %>% 
    mutate(ID=row_number()-1)

Links_source <- Links_source %>% 
    left_join(listing,by=c("source"="name")) %>% 
    left_join(listing,by=c("target"="name")) %>% 
    transmute(source=ID.x,
              target=ID.y,
              value) 

 #my_color <- 'd3.scaleOrdinal() .domain(["a", "b"]) .range(["#EB8C00", "#AA2417"])'
  
  sankeyNetwork(Links = Links_source, Nodes = listing, Source = "source",
                Target = "target", Value = "value", NodeID = "name",
                units = " Employees", fontSize = 12, nodeWidth = 30, 
                colourScale=my_color, 
                iterations = 0)
  
  
  my_color <- 'd3.scaleOrdinal() .domain(["a", "b"]) .range(["#EB8C00", "#AA2417"])'
  
  sankeyNetwork(Links = Links_source, Nodes = listing, Source = "source",
                Target = "target", Value = "value", NodeID = "name",
                units = " Students", fontSize = 12, nodeWidth = 30, 
                #colourScale=my_color, 
                iterations = 0)

```


# Look at the missing salary

Base on below it seems that salary that are not available is linked to the fact that the person was not placed.
Data could then be used for two types of analysis
+ classification problem - who end up place or not place
+ Regression problem - what is the expected starting salary if placed

```{r}

placement %>% 
  select(placement_status,salary) %>% 
  mutate(salary =case_when(is.na(salary)~"Not_Avail",
                           TRUE         ~ "Avail")) %>% 
  count(placement_status,salary)


```


# Dive into the feature distibrution

Salary should get normalization as log distribution the rest is pretty much normalized with exception of employability grade

```{r}

placement %>% 
  select(is.numeric) %>% 
  ggpairs()

```

